When easy is not preferred: A discounting paradigm to assess load-independent task preference

### 2023-02-15 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
replaced one more pilot thing

The sample of the pilot study consisted of $N=15$ participants (53.3% female, $M=24.43$ ($SD=3.59$) years old).
One participant's data was removed because they misunderstood the instruction.
Due to a technical error the subjective task load data of one participant was incomplete, so the hypotheses involving the NASA Task Load Index were analyzed with $n=`r length(setindex)-2`$ data sets.
The results showed increases in subjective and objective task load measures with higher *n*-back level.
Importantly, SVs were lower for higher *n*-back levels, but not different between 1- and 2-back, which shows that the easiest level is not universally preferred.
The LMM revealed *n*-back level as a reliable predictor of SV, even after controlling for declining task performance (*d’* and median RT).
NASA-TLX scores were higher with higher *n*, and lower for the group with lower NFC scores, but NFC and *n*-back level did not interact.
All results are detailed in the Supplementary Material.

>>>>

The sample of the pilot study consisted of $N=15$ participants (53.3% female, $M=24.43$ ($SD=3.59$) years old).
One participant's data was removed because they misunderstood the instruction.
Due to a technical error the subjective task load data of one participant was incomplete, so the hypotheses involving the NASA Task Load Index were analyzed with $n=14$ data sets.
The results showed increases in subjective and objective task load measures with higher *n*-back level.
Importantly, SVs were lower for higher *n*-back levels, but not different between 1- and 2-back, which shows that the easiest level is not universally preferred.
The LMM revealed *n*-back level as a reliable predictor of SV, even after controlling for declining task performance (*d’* and median RT).
NASA-TLX scores were higher with higher *n*, and lower for the group with lower NFC scores, but NFC and *n*-back level did not interact.
All results are detailed in the Supplementary Material.
